Tango-cc analysis

### 2024-05-15 stats/analysis.Rmd
correct small errors (esp. authors)

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(ggpubr) # ggarrange
library(splithalfr) # split half reliability
library(ggridges) # for ridge plot
# load source code for geom_flat_violin()
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

@@

trialtypes_est <- tibble(
  community = rownames(mestimates$community[,,1]),
  Intercept = mestimates$community[, , "Intercept"][1:17],
  Training1 = mestimates$community[, , "trialtypeTraining1"][1:17],
  Training2 = mestimates$community[, , "trialtypeTraining2"][1:17]
)

saveRDS(mtrialtypes, "../saves/mtrialtypes.rds")
saveRDS(trialtypes_est, "../saves/trialtypes_est")
```

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
# library(cmdstanr) # modeling
library(ggpubr) # ggarrange
library(splithalfr) # split half reliability
library(ggridges) # for ridge plot
# load source code for geom_flat_violin()
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

@@

trialtypes_est <- tibble(
  community = rownames(mestimates$community[,,1]),
  Intercept = mestimates$community[, , "Intercept"][1:17],
  Intercept_q25 = mestimates$community[, , "Intercept"][35:51],
  Intercept_q975 = mestimates$community[, , "Intercept"][52:68],
  Training1 = mestimates$community[, , "trialtypeTraining1"][1:17],
  Training1_q25 = mestimates$community[, , "trialtypeTraining1"][35:51],
  Training1_q975 = mestimates$community[, , "trialtypeTraining1"][52:68],
  Training2 = mestimates$community[, , "trialtypeTraining2"][1:17],
  Training2_q25 = mestimates$community[, , "trialtypeTraining2"][35:51],
  Training2_q975 = mestimates$community[, , "trialtypeTraining2"][52:68]
) %>% 
  mutate(across(where(is.numeric), ~round(., 2)))
trialtypes_est

saveRDS(mtrialtypes, "../saves/mtrialtypes.rds")
# mtrialtypes <- readRDS("../saves/mtrialtypes.rds")
saveRDS(trialtypes_est, "../saves/trialtypes_est")
```
